Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Consistency in section names

\subsection{Improved algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for the \OBRP restricted to clusters of capacity $k=2$.
We interpret a pair of nodes collocated in one cluster as a matched pair.
Hence,
the problem is an online variant of the classic matching problem where
a matched pair can separate from each other in order to ``rematch'' with two other nodes.
This is known as the  \emph{Online Rematching} 
problem and a (non-strict) 7-competitive algorithm is already given by \cite{repartition-disc},
in which the ratio comes with an additive factor in $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
In addition,
our algorithm is similar
and slightly simpler than the one in \cite{repartition-disc}, 
while our analysis is significantly more simple and concise,
thanks to the charging scheme we devise here.

>>>>

\subsection{Improved Algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for the \OBRP restricted to clusters of capacity $k=2$.
We interpret a pair of nodes collocated in one cluster as a matched pair.
Hence,
the problem is an online variant of the classic matching problem where
a matched pair can separate from each other in order to ``rematch'' with two other nodes.
This is known as the  \emph{Online Rematching} 
problem and a (non-strict) 7-competitive algorithm is already given by \cite{repartition-disc},
in which the ratio comes with an additive factor in $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
In addition,
our algorithm is similar
and slightly simpler than the one in \cite{repartition-disc}, 
while our analysis is significantly more simple and concise,
thanks to the charging scheme we devise here.
